Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

### 2018-11-26 paper/sections/introduction.tex
ready to send for proof read

New and developing ‘smart’ technologies today provide the infrastructure over
which movements and interactions of people can be measured and monitored in the
‘sentient city’ (Amin and Thrift 2017). This is making it possible to
reinvigorate conceptualise the city as the locus of human activities
supplementing night time geographies of residence (Martin et al 2015) with
geographies of shopping behaviour (Lloyd and Cheshire 2018*), workzone
geographies (Singleton and Longley 2018) and studies of movement trajectories
(Campbell et al 2008). This is rendering activity-based conceptions of human
behaviour central to analysis of hardship and opportunity in and around the
smart city (Venerandi et al 2015).

Sentient technologies include mobile phone networks, which can triangulate user
locations relative to networks of masts, use of GPS to locate users of social
media services, and Wi-Fi access points connectivity to access the Internet.
These technologies offer differing levels of spatial precision, where mobile
telephony and Wi-Fi generally being less reliable and offer lower precision than
GPS to the end users, while being more advantageous for broader mobility studies
(Pinelli et al.  2015). There has been considerable research into the usefulness
of these technologies to understand patterns of movement in cities in near real
time (Candia et al. 2008, Gonzalez et al. 2008, Calabrese et al. 2013).  Most of
this research has focused upon technical specification of accuracy or precision
(Song et al. 2010, Lane et al. 2010), with somewhat less attention devoted to
the ways that the characteristics of the technologies and of their human users
conspire to create possible bias in representing usage patterns across the
entire smart city.

>>>>

New and developing ‘smart’ technologies today provide the infrastructure over
which movements and interactions of people can be measured and monitored in the
‘sentient city’ \citep{amin2017seeing}. This is making it possible to
reinvigorate conceptualise the city as the locus of human activities
supplementing night time geographies of residence \citep{martin2015developing}
with geographies of shopping behaviour \citep{lloyd2018detecting}, workzone
geographies \citep{singleton2018london} and studies of movement trajectories
\citep{campbell2008transforming}. This is rendering activity-based conceptions
of human behaviour central to analysis of hardship and opportunity in and
around the smart city \citep{venerandi2015measuring}.

Sentient technologies include mobile phone networks, which can triangulate user
locations relative to networks of masts, use of GPS to locate users of social
media services, and Wi-Fi access points connectivity to access the Internet.
These technologies offer differing levels of spatial precision, where mobile
telephony and Wi-Fi generally being less reliable and offer lower precision
than GPS to the end users, while being more advantageous for broader mobility
studies \citep{pinelli2015comparing}. There has been considerable research into
the usefulness of these technologies to understand patterns of movement in
cities in near real time \citep{candia2008uncovering,
gonzalez2008understanding, calabrese2013understanding}.  Most of this research
has focused upon technical specification of accuracy or precision
\citep{song2010limits,lane2010survey}, with somewhat less attention devoted to
the ways that the characteristics of the technologies and of their human users
conspire to create possible bias in representing usage patterns across the
entire smart city.
